---
title: "Selection temp"
author: "Josquin Daron"
date: "5 octobre 2021"
output:
  pdf_document: default
  html_document: default
---

# Selection analysis

```{r 1Pop, eval=FALSE}
popStatsDescWindows.py --snp wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ -b bed  -o LBVwil --keep LBVwil.ind -a accessibility.h5 -wt snp -w 500
popStatsDescWindows.py --snp wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ -b bed  -o LPdom --keep LPdom.ind -a ag1000g/accessibility.h5 -wt snp -w 500
popStatsDescWindows.py --snp wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ -b bed  -o LPfor --keep LPfor.ind -a ag1000g/accessibility.h5 -wt snp -w 500
```

```{r 2Pop, eval=FALSE}
fst_scan.py --zarr wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ --pop1 LPdom.ind --pop2 LPfor.ind -o LPdom_LPfor -w 500
fst_scan.py --zarr wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ --pop1 LPdom.ind --pop2 LBVwil.ind -o LPdom_LBVwil -w 500
fst_scan.py --zarr wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ --pop1 LPfor.ind --pop2 LBVwil.ind -o LPfor_LBVwil -w 500
```


```{r 3Pop, eval=FALSE}
getPBS_scan.py --pop1 LPdom.ind --pop2 LPfor.ind --pop3 LBVwil.ind --zarr wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ -o LPdom_LPfor_LBVwil -w 500
getPBS_scan.py --pop1 LBVwil.ind --pop2 LPdom.ind --pop3 LPfor.ind --zarr wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ -o LBVwil_LPdom_LPfor -w 500
getPBS_scan.py --pop1 LBVwil.ind --pop2 LPfor.ind --pop3 LPdom.ind --zarr wilding.unifiedGenotyper.cov14x.passQC.phased.zarr/ -o LBVwil_LPfor_LPdom -w 500
```

#############
### 1pop stat
#############

windows size = 20kb
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.1pop.stats.20kbw.pdf}
\end{center}

windows size = 1000snp
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.1pop.stats.1000snp.pdf}
\end{center}

#############
### 2pop stat
#############


windows size = 1000snp
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.2pop.stats.1000snp.pdf}
\end{center}

windows size = 500snp
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.2pop.stats.500snp.pdf}
\end{center}

### PBS

windows size = 1000snp
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.3pop.stats.1000snp.pdf}
\end{center}

windows size = 500snp
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.3pop.stats.500snp.pdf}
\end{center}

windows size = 250snp
\begin{center}
\includegraphics[width=7in]{/home/daron/bioInf/wilding/selection/wilding.3pop.stats.250snp.pdf}
\end{center}
